Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond to reviewer wrt unfeasible sliding path.

The previous section has presented a simple algorithm that solves manipulation planning
problems on a given constraint manifold of $\mathcal{C}$.

If we use this algorithm with static 
balance constraints without fixing globally the robot foot positions, it generates 
statically balanced paths for a robot sliding on the ground. Fig~\ref{fig:sliding} shows
an example of a whole-body collision-free path for a robot passing between two chairs.
Such paths are physically unfeasible. They are, however, easier to generate than feasible
dynamic trajectories because only geometric constraints are considered at planning time.

>>>>

The previous section has presented a simple algorithm that solves
manipulation planning problems on a given constraint manifold
$\manifold$ of $\mathcal{C}$.

If we use this algorithm with static balance constraints without
fixing globally the robot foot positions, it generates statically
balanced paths for a robot \textit{sliding} on the
ground. \textbf{Fig~\ref{fig:sliding} shows an example of a whole-body
  collision-free path for a robot passing between two chairs. Since in
  reality a legged robot cannot slide on a regular floor, such paths
  are physically unfeasible.They are, however, easier to generate than
  feasible dynamic walking trajectories because only geometric
  constraints are considered at planning time.}
